SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-11-25 toplas26/examples.tex
checkpoint

In the \ttt{mult} function, each client $\ttt{i}$ symmetrically
computes:
$$
\ttt{((m[z++"d"] * m[y]) + (-m[z++"e"] * m[z++"a"]) + m[z++"c"])@i}
$$
Since $\ttt{m[z++"d"]@i\,:\,public}\ $ and $\ \ttt{m[z++"e"]@i\,:\,public}$
are both established by $\ttt{secopen}$, and
$\ttt{m[y]@i}$, $\ttt{m[z++"a"]@i}$, and $\ttt{m[z++"c"]@i}$ are
all declared to be shares in preconditions, we have that each
of the shared computations $\ttt{(m[z++"d"] * m[y])@i}$ and $\ttt{(-m[z++"e"] * m[z++"a"])@i}$
are shares, so the gate outputs are shares, and this will
be successfully checked by syntax-directed $\Vdash$ type checking that
results from the declaration $\ttt{[m[z]@i1,m[z]@i2]\,:\,shares}$.

>>>>

In the \ttt{mult} function, each client $\ttt{i}$ symmetrically
computes:
$$
\ttt{((m[z++"d"] * m[y]) + (-m[z++"e"] * m[z++"a"]) + m[z++"c"])@i}
$$
Since $\ttt{m[z++"d"]@i\,:\,public}\ $ and $\ \ttt{m[z++"e"]@i\,:\,public}$
are both established by $\ttt{secopen}$, and
$\ttt{m[y]@i}$, $\ttt{m[z++"a"]@i}$, and $\ttt{m[z++"c"]@i}$ are
all declared to be shares in preconditions, we have that each
of the shared computations $\ttt{(m[z++"d"] * m[y])@i}$ and $\ttt{(-m[z++"e"] * m[z++"a"])@i}$
are shares, so the gate outputs, which are then sums of shares, are shares, and this will
be successfully checked by syntax-directed $\Vdash$ type checking that
results from the declaration $\ttt{[m[z]@i1,m[z]@i2]\,:\,shares}$.
